---
title: 'Assignment 2 Task 2: Parameter Estimation with Purrr'
author: "Matthieu Huy"
date: "2023-02-11"
output: html_document
---

```{r setup, echo = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(tidymodels)
library(kableExtra)
library(here)
library(cowplot)
library(GGally)
library(AICcmodavg)
library(jtools)
```

This analysis uses data containing observations of lizard species, sex, length, and weight in the Jornada Basin, located in the Chihuahaun desert of New Mexico.

Citation:\
- Lightfoot, D. and W.G. Whitford. 2020. Lizard pitfall trap data from 11 NPP study locations at the Jornada Basin LTER site, 1989-2006 ver 37. Environmental Data Initiative. https://doi.org/10.6073/pasta/4a6e258fb49c31e222ecbbcfd128967f (Accessed 2023-02-11).


Metadata:\
- https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-jrn.210007001.37


For this analysis, I will use non linear least squares to estimate parameters of a length to weight model for lizard populations in New Mexico. 

### Read in and clean data 

```{r}
lizards_data <- read_csv(here("data/lizards.csv")) |>
  janitor::clean_names() |>
  rename(length = sv_length, species = spp)

lizard_species_code <- read_table(here("data/Lizardcodelist.txt"), col_names = FALSE) |>
  unite(scientific_name, X2, X3) |>
  unite(common_name, X4, X5, X6) |>
  select(code = X1, scientific_name, common_name) |>
  tail(19)
```


